---
title: "project"
author: "Team Omega"
date: "December 3, 2017"
output: pdf_document
---

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###loading libraries

suppressWarnings(library(dplyr))
suppressWarnings(library(purrr))
suppressWarnings(library(knitr))
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###loading dataset
load("paintings_train.Rdata")
train <- paintings_train
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###select variables

#Professor's recoding
train <- train %>%
  mutate(shape_recode = ifelse(Shape == "", "Not Available",
                               ifelse(Shape == "ovale", "oval",
                                      ifelse(Shape == "ronde", "round",
                                             ifelse(Shape == "octogon", "octagon", Shape)))))

#recode
train <- train %>%
  mutate(mat_recode = ifelse(mat %in% c("a", "bc", "c","br"), "metal",
                      ifelse(mat %in% c("al", "ar", "m"), "stone",
                      ifelse(mat %in% c("co", "bt", "t","h","ta"), "canvas",
                      ifelse(mat %in% c("p", "ca"), "paper",
                      ifelse(mat %in% c("b"), "wood",
                      ifelse(mat %in% c("o", "e","v","mi","pa","g"), "other",
                      ifelse(mat %in% c("n/a", ""), "uncertain", NA))))))))

train <- train%>%
  mutate(fig_mention = ifelse(nfigures ==0, "no figures", "figures"))

train <- train%>%
  mutate(artist_living_notliving = ifelse(artistliving==0, "not living", "living"))

train <- train%>%
  mutate(history_nohistory = ifelse(history==0, "no history", "history"))

train <- train%>%
  mutate(mytho_nomytho = ifelse(mytho==0, "no mytho", "mytho"))

train <- train%>%
  mutate(finished_nofinished = ifelse(finished==0, "no finished", "finished"))

train <- train%>%
  mutate(LF = ifelse(lrgfont==0, "no LF", "LF"))

#remove completely descriptive (thus irrelevant) variables
newTrain <- train[,!names(train) %in% c("sale","lot","position","logprice","subject",
                                        "authorstyle","authorstandard","author",
                                        "winningbidder",
                                        "Interm","Height_in","Width_in","Surface_Rect",
                                        "Diam_in","Surface_Rnd","material","mat",
                                        "lands_sc","lands_elem","lands_figs","lands_ment")]

#put price as the first column
newTrain <- newTrain[,c(7,1:6,8:46)]

#change price into numeric
newTrain$price <- as.numeric(gsub(",","",newTrain$price))

#NA
which(apply(newTrain,2,anyNA) == TRUE)

#remove NA
newTrain <- newTrain[complete.cases(newTrain$Surface),]

#change all character strings to factors
character_vars <- lapply(newTrain, class) == "character"
newTrain[, character_vars] <- lapply(newTrain[, character_vars], as.factor)

#change the level of factor
levels(newTrain$type_intermed)[levels(newTrain$type_intermed)==""] <- "NONE"
levels(newTrain$winningbiddertype)[levels(newTrain$winningbiddertype)==""] <- "NONE"
levels(newTrain$endbuyer)[levels(newTrain$endbuyer)==""] <- "NONE"
levels(newTrain$materialCat)[levels(newTrain$materialCat)==""] <- "NONE"
levels(newTrain$school_pntg)[levels(newTrain$school_pntg)=="S"] <- "OTHER"
levels(newTrain$winningbiddertype)[levels(newTrain$winningbiddertype)=="EBC"] <- "OTHER"

#centering
newTrain$year <- scale(newTrain$year, center = TRUE, scale = TRUE)
newTrain$Surface <- scale(newTrain$Surface, center = TRUE, scale = TRUE)
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###testing dataset
load("paintings_test.Rdata")
test <- paintings_test

#recode
test <- test %>%
  mutate(mat_recode = ifelse(mat %in% c("a", "bc", "c","br"), "metal",
                      ifelse(mat %in% c("al", "ar", "m"), "stone",
                      ifelse(mat %in% c("co", "bt", "t","h","ta"), "canvas",
                      ifelse(mat %in% c("p", "ca"), "paper",
                      ifelse(mat %in% c("b"), "wood",
                      ifelse(mat %in% c("o", "e","v","mi","pa","g"), "other",
                      ifelse(mat %in% c("n/a", ""), "uncertain", NA))))))))

test <- test%>%
  mutate(fig_mention = ifelse(nfigures ==0, "no figures", "figures"))

test <- test%>%
  mutate(artist_living_notliving = ifelse(artistliving==0, "not living", "living"))

test <- test%>%
  mutate(history_nohistory = ifelse(history==0, "no history", "history"))

test <- test%>%
  mutate(mytho_nomytho = ifelse(mytho==0, "no mytho", "mytho"))

test <- test%>%
  mutate(finished_nofinished = ifelse(finished==0, "no finished", "finished"))

test <- test%>%
  mutate(LF = ifelse(lrgfont==0, "no LF", "LF"))


#Professor's recoding
test <- test %>%
  mutate(shape_recode = ifelse(Shape == "", "Not Available",
                               ifelse(Shape == "ovale", "oval",
                                      ifelse(Shape == "ronde", "round",
                                             ifelse(Shape == "octogon", "octagon", Shape)))))

newTest <- test[,!names(test) %in% c("sale","lot","position","logprice","subject",
                                        "authorstyle","authorstandard","author",
                                        "winningbidder", "price",
                                        "Interm","Height_in","Width_in","Surface_Rect",
                                        "Diam_in","Surface_Rnd","material","mat",
                                        "lands_sc","lands_elem","lands_figs","lands_ment")]

#change all character strings to factors
character_vars <- lapply(newTest, class) == "character"
newTest[, character_vars] <- lapply(newTest[, character_vars], as.factor)

#change the level of factors
levels(newTest$type_intermed)[levels(newTest$type_intermed)==""] <- "NONE"
levels(newTest$winningbiddertype)[levels(newTest$winningbiddertype)==""] <- "NONE"
levels(newTest$endbuyer)[levels(newTest$endbuyer)==""] <- "NONE"
levels(newTest$materialCat)[levels(newTest$materialCat)==""] <- "NONE"
levels(newTest$school_pntg)[levels(newTest$school_pntg)=="A"] <- "OTHER"
levels(newTest$school_pntg)[levels(newTest$school_pntg)=="G"] <- "OTHER"
levels(newTest$winningbiddertype)[levels(newTest$winningbiddertype)=="EBC"] <- "OTHER"
levels(newTest$winningbiddertype)[levels(newTest$winningbiddertype)=="BB"] <- "OTHER"
levels(newTest$winningbiddertype)[levels(newTest$winningbiddertype)=="ED"] <- "OTHER"

#simple method to predict the NA in surface
newTest$Surface[which(is.na(newTest$Surface)==TRUE)] <- mean(newTest$Surface, na.rm = TRUE)

#centering
newTestn$year <- scale(newTest$year, center = TRUE, scale = TRUE)
newTest$Surface <- scale(newTest$Surface, center = TRUE, scale = TRUE)
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
#initial model with logging price
m1 <- lm(log(price) ~ .,dat=newTrain)
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###AIC
best_AIC <- step(m1,direction = "both",k=2)
summary(best_AIC)
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###BIC
best_BIC <- step(m1,direction = "both",k=log(nrow(newTrain)))
summary(best_BIC)
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
###Testing Push
m <- lm(formula = log(price) ~ dealer + year + school_pntg + diff_origin + 
        artistliving + winningbiddertype + Surface + engraved + 
        prevcoll + paired + finished + lrgfont + othgenre +  
        discauth + winningbiddertype:prevcoll + 
        Surface:mat_recode, data = newTrain)
```

```{r,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
predictions = as.data.frame(
  exp(predict(m, newdata=newTest, 
              interval = "pred")))
save(predictions, file="predict-test.Rdata")
```

### Part I Write up *Due Dec 7*

3. Development and assessment of an initial model (10 points)

* Initial model: must include a summary table and an explanation/discussion for variable selection and overall amount of variation explained. 

* Model selection: must include a discussion

* Residual: must include residual plot(s) and a discussion.  

* Variables: must include table of coefficients and CI

4. Summary and Conclusions (10 points)

What is the (median) price for the "baseline" category if there are categorical or dummy variables in the model (add CI's)?  (be sure to include units!) Highlight important findings and potential limitations of your model.  Does it appear that interactions are important?  What are the most important variables and/or interactions?  Provide interprations of how the most important variables influence the (median) price giving a range (CI).  Correct interpretation of coefficients for the log model desirable for full points.

Provide recommendations for the art historian about features or combination of features to look for to find the most valuable paintings.

_Points will be deducted for code chunks that should not be included, etc._

*Upload write up  to Sakai*

#Introduction: 

#Summary of Problem: 
We are given a dataset which provides information about auctions of paintings which were sold between years 1764 and 1780. The data tells us about different attributes of paintings, information about auction, information about the artist, information about the buyer and the price at which it was sold. There are total 59 columns (variables) in data including 'price' and 'log(price)'. Our task is to find out the relation between variables and the price so that we can predict the price of a paintings. We should also interpret the results as which are the most/least influential factor in determining the price of the painting. 

Objectives:
1) Exploratory data analysis
2) Find out interaction
3) Create a model with 10-20 most influential factors and interpret results
4) Test the model with test data and interpret the results 


#Exploratory Data Analysis

#Variables which we think are not importanat in predicting the price
1) sale - We have sepater variables for dealer code and year
2) materialCat- 
3) subject- Too many levels in a simple model 
4) authorstandard- Too many variable in a simple model
5) authorstyle - n/a for most of the values
6) winningbidder- Too many variable in a simple model
7) surface_rect- We have separate variable for 'surface' and 'shape'
8) surface_rnd- We have separate variable for 'surface' and 'shape'


# Some Graphs and analysis
1)  


#Development and assessment of an initial model (10 points)

* Initial model: must include a summary table and an explanation/discussion for variable selection and overall amount of variation explained. 

```{r,eval=FALSE}
summary(m)
```

As we observe from the summary, the first part we notice is that there are several NA values in some layers of our interaction terms, because the training dataset may not have data to back up the layer, thus generating NA values. After that, we can interpret the coefficients of categorical variables in a sense that when the variable is changed from 0 (reference level) to 1, the value of log(price) will change by an amount of $\beta$. For example, the variable "lrgfont" has a coefficient 9.080e-01. This means that if we change "lrgfont" from 0 to 1 (ie. if the dealer devotes an additional paragraph), then on average, the log(price) will increase by 9.080e-01, which in turn translates to an increase of $\exp^{9.080e-01}=2.479359$ livres. For continuous variable, such as "Surface", the coefficient represent that for every 1 unit increase in predictor, we expect the price to change by an amount of $\beta$. For example, the variable "Surface"     


###Model selection

Since we are given a dataset with 59 variables (including 'price' and 'log(pirce)'), a model that includes all of them will be too complicated and run into the risk of overfitting. Therefore, we decide to do model selection by removing some variables that may not help our prediction. We carry out the model selection by four steps: recoding, general analysis, BIC, and interaction.

To begin with, we decide to recode some variables to better represent their respective features. Besides the recode of 'shape_recode' provided by Professor, we also generate some recode variables: 'mat_recode', 'fig_mention', 'artist_living_notliving', 'history_nohistory', 'mytho_nomytho', 'finished_nofinished', and 'LF'. In particular, in 'mat_recode', we recode "a" (silver), "bc" (wood and copper), "c" (copper),"br" (bronze frames) into "metal"; "al" (alabaster), "ar" (slate), "m" (marble) into "stone"; "co" (cloth), "bt" (canvas), "t" (canvas),"h" (oil technique),"ta" (canvas) into "canvas"; "p" (paper), "ca" (cardboard) into "paper"; "b" (wood) into "wood"; "o" (other), "e" (wax),"v" (glass),"mi" (miniature technique),"pa" (pastel),"g" (grissaille technique) into "other"; the rest into "uncertain". For the other recode variables, we use them as indicators of corresponding features (0 if the feature does not exist, and 1 if it does).

After recoding, we remove some variables which we believe are not contributing to our model or are repetitive. After careful analysis, we decide to remove "sale", "lot", "position", "logprice", "subject", "authorstyle", "authorstandard", "author", "winningbidder", "Interm", "Height_in", "Width_in", "Surface_Rect", "Diam_in", "Surface_Rnd", "material", "mat", "lands_sc", "lands_elem", "lands_figs", and "lands_ment". In particular, we remove "sale" because it is a combination of dealer and year, both of which we have included in our raw model. We remove "lot" and "position" because they are identifiers of paintings, which we believe are not helpful in linear modeling. We remove "logprice" because we can just take log(price). We remove "subject" because it is descriptive, and even though we may be able to use some Natural Language Processing (NLP) knowledge to understand this feature better, this is out of the scope of our current task. We remove "authorstyle" because this variable contains too many n/a, which itself has no meaning (sometimes, a value is missing for some particular reason, but in this case we do not think so), and we have very few method to interpret these n/a values. We remove both "authorstandard" and "author" because they contain too many layers; while they could be useful predictors if studied carefully (paintings associated with certain authors may be more expensive than others), we decide to drop them as we do not have sufficient information about each of them. We remove "winningbidder" because its information is conveyed by "winningbiddertype". We remove "Interm" for the same reason as previous one. We remove "Height_in", "Width_in", "Surface_Rect", "Diam_in", and "Surface_Rnd" because their information can be conveyed by "Surface". Similarly, we remove "material", "mat", "lands_sc", "lands_elem", "lands_figs" becasue their information can be conveyed by "mat_recode" and "landsALL", respectively.

After all of the preparation, we run AIC and BIC analysis on our raw model, which includes all the variables remaining. In the end, we decide to use BIC analysis, and use the final model generated from BIC analysis as our first step to understand the dataset using linear models. The model obtained after BIC analysis is as follow:

"log(price) ~ dealer + year + school_pntg + diff_origin + artistliving + winningbiddertype + Surface + nfigures + engraved + prevcoll + othartist + paired + finished + lrgfont + othgenre + discauth"

After this, as we use the model obtained from BIC analysis to study the dataset, we slowly remove some of the variables, such as "othartist" and "nfigures", which we believe do not contribute much in our model. Later on, we also study the interaction effect between the predictors ("winningbiddertype:prevcoll"). We even go back to our initial model and manage to find an important interaction term between a predictor and a variable that seems insignificant on its own (Surface:mat_recode). Eventually, we finalize our model as follow:

"log(price) ~ dealer + year + school_pntg + diff_origin + artistliving + winningbiddertype + Surface + engraved + prevcoll + paired + finished + lrgfont + othgenre + discauth + winningbiddertype:prevcoll + Surface:mat_recode"

###Residual  

```{r, echo=FALSE}
par(mfrow = c(2, 2))
plot(m)
par(mfrow = c(1, 1))
```

As we observe from the residual plots, we see a straight horizontal line, around which there is a patternless cloud of points. This shows that the independence assumption of linear model is well followed.

###Table of coefficients and CI

```{r, echo=FALSE}
ci <- confint(m, level = 0.95)
table_coef <- as.data.frame(cbind(getElement(summary(m), "coefficients")[,"Estimate"],
                                  ci[complete.cases(ci[,"2.5 %"]),]))
colnames(table_coef)[1] <- "Estimate"
kable(table_coef, digits = 2)
```

4. Summary and Conclusions (10 points)

What is the (median) price for the "baseline" category if there are categorical or dummy variables in the model (add CI's)?  (be sure to include units!) Highlight important findings and potential limitations of your model.  Does it appear that interactions are important?  What are the most important variables and/or interactions?  Provide interprations of how the most important variables influence the (median) price giving a range (CI).  Correct interpretation of coefficients for the log model desirable for full points.

Provide recommendations for the art historian about features or combination of features to look for to find the most valuable paintings.

```{r}
summary(m)
```

Based on the summary, the intercept is 3.159 livres. This means that when every categorical variable is at its reference level, and continuous 

From our summary, it seems that dealer and winningbiddertype affect the price the most, as they have the largest estimate. This is expected, because different dealers may have the price differently, or even may have different sources of painting to sell, thus resulting in different price ranges (ie. some dealers may have sources of highly-sought paintings, whereas other dealers may just have normal paintings). The same reasoning applies to "winningbiddertype" as well. When a dealer on behalf of collector is buying a painting, he will definitely have a different ulterior agenda in mind from, say, a buy himself. 

One of the potential limitations about our model is that we may not be able to consider every single possible combination of interation terms. In fact, as we analyze the dataset, we only consider interaction between two variables. However, interactions can occur even with multiple variables, and our model does not consider EVERY SINGLE of these potentially significant multiple interactions.

According to our summary, we believe that 