---
title: "project_chinmay"
author: "Chinmay Ajnadkar"
date: "12/7/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Importing Libraries
```{r}
library(ggplot2)
library(dplyr)
library(stringr)
library(GGally)
```

Reading data and putting it as a variable
```{r read-data, echo=TRUE}
load("paintings_train.Rdata")
train = paintings_train
```

Summary of dataframe
```{r}
dim(train)
```
1131 rows and 59 columns in the data. 


#Dropping Following variables from training data
sale
subject
authorstandard
authorstyle - n/a for most of the values
winningbidder
surface_rect
surface_rnd
materailCat

```{r}
drops <- c("sale", "subject","authorstandard", "authorstyle", "winningbidder", "Surface_Rect", "Surface_Rnd", "materialCat")
train <- train[, !(names(train) %in% drops)]
```

Now we have 50 predictors to choose from.


#Transforming some Variables:
1) We will create another variable 'shape_recode' to recode shape
```{r}
train <- train %>%
  mutate(shape_recode = ifelse(Shape == "", NA,
                        ifelse(Shape == "ovale", "oval",
                        ifelse(Shape == "ronde", "round", Shape))))

train <- subset(train, select = -c(Shape))
```

2) We will create another variable 'mat_recode' to reode materials
```{r}
train <- train %>%
  mutate(mat_recode = ifelse(mat %in% c("a", "bc", "c","br"), "metal",
                      ifelse(mat %in% c("al", "ar", "m"), "stone",
                      ifelse(mat %in% c("co", "bt", "t","h"), "canvas",
                      ifelse(mat %in% c("p", "ca"), "paper",
                      ifelse(mat %in% c("b"), "wood",
                      ifelse(mat %in% c("o", "e","v","mi","pa","g"), "other",
                      ifelse(mat %in% c("n/a", ""),"uncertain",NA))))))))

#train <- subset(train, select = -c(mat))
```

3)Fixing Prices
```{r}
train <- train %>%
  mutate(price = as.numeric(str_replace(price, ",","")))

```


4)Figure/No_figure categorical variable
```{r}
train <- train%>%
  mutate(fig_mention = ifelse(nfigures ==0, "no figures", "figures"))

```

5) Artist_living_noliving
```{r}
train <- train%>%
  mutate(artist_living_notliving = ifelse(artistliving==0, "not living", "living"))
```

6) History_nohistory
```{r}
train <- train%>%
  mutate(history_nohistory = ifelse(history==0, "no history", "history"))
```

7) Mytho_nomytho
```{r}
train <- train%>%
  mutate(mytho_nomytho = ifelse(mytho==0, "no mytho", "mytho"))
```

8) finished_nofinished
```{r}
train <- train%>%
  mutate(finished_nofinished = ifelse(finished==0, "no finished", "finished"))
```

9)
```{r}
train <- train%>%
  mutate(LF = ifelse(finished==0, "no LF", "LF"))

```


#EDA 

1) 'origin_cat' distribution
```{r}
table(train$origin_cat)
```

2) Shapes of painting
```{r}
train %>% 
  group_by(shape_recode)%>% 
  summarise(count =n()) %>%
  arrange()
```

3)
```{r}
train %>% 
  group_by(fig_mention, nfigures) %>%
  summarise(n())

```


```{r}
ggplot (data= train, aes (y = price, x = fig_mention, col = fig_mention))+
  geom_boxplot() 
```

```{r}
ggplot (data= train, aes (y = price, x = fig_mention, col = fig_mention))+
  geom_boxplot() +
  scale_y_log10()
```

Conclusion : Paintings with figures have higher average price than paintings with no figures

4) Material category side-by-side boxplots
```{r}
ggplot (data= train, aes (y = price, x = mat_recode , col = mat_recode))+
  geom_boxplot() +
  scale_y_log10()
```


5) Artist Living or not
```{r}
ggplot (data= train, aes (y = price, x =  artist_living_notliving, col = artist_living_notliving))+
  geom_boxplot() +
  scale_y_log10()
```

6) Surface area 
```{r}
ggplot(data = train, aes(x = year, y = logprice)) + geom_point() + stat_smooth(method = "lm")
m1 <- lm(logprice ~ year, data = train)
summary(m1)
```


7) Surface and price
```{r}
ggplot(data = train, aes(x = Surface, y = logprice)) + geom_point() + stat_smooth(method = "lm")
m1 <- lm(logprice ~ Surface, data = train)
summary(m1)
```

8) nfigures and price
```{r}
ggplot(data = train, aes(x = nfigures, y = logprice)) + geom_point() + stat_smooth(method = "lm")
m1 <- lm(logprice ~ nfigures, data = train)
summary(m1)

```

9) 
```{r}
ggplot (data= train, aes (y = price, x =  finished_nofinished, col = finished_nofinished))+
  geom_boxplot() +
  scale_y_log10()
```

10)
```{r}
ggplot (data= train, aes (y = price, x = mytho_nomytho , col = mytho_nomytho ))+
  geom_boxplot() +
  scale_y_log10()
```
11) 
```{r}
ggplot (data= train, aes (y = price, x =  history_nohistory, col = history_nohistory))+
  geom_boxplot() +
  scale_y_log10()
```

12)
```{r}
ggplot (data= train, aes (y = price, x =  LF, col = LF))+
  geom_boxplot() +
  scale_y_log10()
```


Possible interactions:
1) Height_in Width_in
2) Price, Surface and artist living or not 
2) Price, Surface and finished
3) Landscape and paired paintings
6) dealer and previous owner
7) winning bidder and previous owner
8) winning bidder and artist living


#Checking Interactions

1)Height and width
```{r}
ggplot(data = train, aes(x = Width_in, y = Height_in)) + geom_point() + stat_smooth(method = "lm")

```

Clearly there is some interaction between heighth and width.

```{r}
m1 <- lm(Height_in ~ Width_in, data = train)
summary(m1)
```

Coeficient is 0.82 with a very small p-value. It proves there is an interaction between height and width.

2) Price, Surface and artist living or not
```{r}
ggplot(data = train, aes(y = logprice, x= Surface, factor= artistliving, color=factor(artistliving))) + geom_point (alpha = 0.3) +
  geom_point(alpha = 0.3) + stat_smooth(method = "lm", fullrange =TRUE)
m1 <- lm(logprice ~ Surface * factor(artistliving), data = train)
summary(m1)
```


3) Price , surface and finished
```{r}
ggplot(data = train, aes(y = logprice, x= Surface, factor= finished, color=factor(finished))) + geom_point (alpha = 0.3) +
  geom_point(alpha = 0.3) + stat_smooth(method = "lm", fullrange =TRUE)
m1 <- lm(logprice ~ Surface * factor(finished), data = train)
summary(m1)
```


2) School of paintings and landscape variable 
```{r}
train2$school_pntg <- factor(train2$school_pntg)
m2 <- lm(logprice ~ as.factor(school_pntg) + landsALL + lands_elem + lands_sc + lands_ment +lands_figs + school_pntg * landsALL + school_pntg * lands_elem + school_pntg * lands_ment + school_pntg * lands_sc + school_pntg * lands_figs, data = train, na.action = na.omit, family = binomial)
summary(m2)



```


3) 

### EDA

Using EDA and any numerical summaries get to know the data -  identify what you might consider the 10 best variables for predicting `logprice` using scatterplots with other variables represented using colors or symbols, scatterplot matrices or conditioning plots.  

### Build your first model

In the first model predict the auction price `price` using the transformation `logprice` using at least 10 up to 20 predictors and any interactions to build a model using linear regression.  You may use stepwise model selection to simplify the model using AIC and/or BIC.  For reference, we will fit the null model to initialize the leaderboard, but replace model1 with your recommended model.


```{r model1, echo=TRUE}
model1 = lm(logprice ~ 1, data=paintings_train)
```


Save predictions and intervals
```{r predict-model1, echo=FALSE}
predictions = as.data.frame(
  exp(predict(model1, newdata=paintings_test, 
              interval = "pred")))
save(predictions, file="predict-test.Rdata")
```


### Part I Write up *Due Dec 7*

Once you are satisfied with your model, provide a write up of your data analysis project in a new Rmd file/pdf file: `Part-I-Writeup.Rmd` by copying over salient parts of your R notebook. The written assignment consists of five parts:

1. Introduction: Summary of problem and objectives (5 points)

2. Exploratory data analysis (10 points): must include three correctly labeled graphs and an explanation that highlight the most important features that went into your model building.

3. Development and assessment of an initial model (10 points)

* Initial model: must include a summary table and an explanation/discussion for variable selection and overall amount of variation explained. 

* Model selection: must include a discussion

* Residual: must include residual plot(s) and a discussion.  

* Variables: must include table of coefficients and CI

3. Summary and Conclusions (10 points)

What is the (median) price for the "baseline" category if there are categorical or dummy variables in the model (add CI's)?  (be sure to include units!) Highlight important findings and potential limitations of your model.  Does it appear that interactions are important?  What are the most important variables and/or interactions?  Provide interprations of how the most important variables influence the (median) price giving a range (CI).  Correct interpretation of coefficients for the log model desirable for full points.

Provide recommendations for the art historian about features or combination of features to look for to find the most valuable paintings.

_Points will be deducted for code chunks that should not be included, etc._

*Upload write up  to Sakai*

###  Evaluation on test data for Part I

Once your write up is submitted, your models will be evaluated on the following criteria based on predictions  on the test data (20 points): 

* Bias:  Average (Yhat-Y)  positive values indicate the model tends to overestimate price (on average) while negative values indicate the model tends to underestimate price.

* Maximum Deviation:  Max |Y-Yhat| -  identifies the worst prediction  made in the validation data set.

* Mean Absolute Deviation:  Average |Y-Yhat| - the average error (regardless of sign).

* Root Mean Square Error: Sqrt Average (Y-Yhat)^2

* Coverage:  Average( lwr < Y < upr) 

In order to have a passing wercker badge, your file for predictions needs to be the same length as the test data, with three columns:  fitted values, lower CI and upper CI values in that order with names, fit, lwr, and upr respectively.  

You will be able to see your scores on the score board.  They will be initialized by a prediction based on the mean in the training data.


## Part II: Complex Model

In this part you may go all out for constructing a best fitting model for predicting housing prices using methods that we have covered this semester.  You should feel free to to create any new variables (such as quadratic, interaction, or indicator variables, splines, etc) and try different methods, keeping in mind you should be able to explain your methods and results.

Update your predictions using your complex model to provide point estimates and CI.

```{r predict-model2, echo=FALSE}
# replace model1 with model2 here
predictions = as.data.frame(
  exp(predict(model1, newdata=paintings_test, 
              interval = "pred")))
save(predictions, file="predict-test.Rdata")
```

You may iterate here as much as you like exploring different models until you are satisfied with your results, however keep in mind you must be able to explain your results to the art historian.

### Part II: Write Up

Once you are satisfied with your model, provide a write up of your data analysis project in a new Rmd file/pdf file: `Part-II-Writeup.Rmd` by copying over salient parts of your R notebook and the previous writeup (you should also save the pdf version) The written assignment consists of five parts:

1. Introduction (1 point if improved from before)
  add previous intro with any edits

2. Exploratory data analysis (1 point if improved from before): 
   add previous EDA
   
3. Discussion of preliminary model Part I (5 points)
Discuss performance based on leader board results and suggested refinements.

4.  Development of the final model (20 points)

* Final model: must include a summary table

* Variables: must include an explanation

* Variable selection/shrinkage: must use appropriate method and include an explanation


* Residual: must include a residual plot and a discussion

* discussion of how prediction intervals obtained 

5. Assessment of the final model (25 points)


* Model evaluation: must include an evaluation discussion

* Model testing : must include a discussion

* Model result: must include a selection and discussion of the top 10 valued  paintings in the validation data.

6. Conclusion (10 points): must include a summary of results and a discussion of things learned. Optional what would you do if you had more time.



### Final Predictions Validation (20 points)
Create predictions for the validation data from your final model using the dataframe `paintings_validation.Rdata` in your repo.  You may refit your final model to the combined training and test data.  Write predictions out to a file `prediction-validation.Rdata`
This should have the same format as the model output in Part I and II.


## Final: Class Presentations and Peer Evaluation

Each Group should prepare 5 slides in their Github repo:  (save as slides.pdf)

* Most interesting graphic  _a picture (painting) is worth a thousand words prize!_  

* Best Model (motivation, how you found it, why you think it is best)

* Best Insights into predicting Price.

* 3 Best Paintings to purchase  (and why) (images are a bonus!)

* Best Team Name/Graphic

We will select winners based on the above criteria and overall performance.


Finally your repo should have: `Part-I-Writeup.Rmd`, `Part-I-Writeup.pdf`,  `Part-II-Writeup.Rmd`, `Part-II-Writeup.pdf`,`slides.Rmd` (and whatever output you use for the presentation) and `predict-train.Rdata`,  `predict-test.Rdata` `predict-validation.Rdata`.
